M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-05-11 notes/thesis-latex-template/thesis.tex
Review after exam.

In order to define the fluxes on the boundaries of each control volume, we employ the 
conservative formulation of the governing equations above. 
The flux terms are defined using finite differences and linear interpolation of the disrete 
variables (defined at the centroid of each cell), except for the advection flux which should not be 
discretized using linear interpolation -- due to a numerical instability 
for large cell Peclet numbers \cite{strikwerda2004finite}.

@@

\subsection{Spherical Coordinates}
Because the system is axisymmetric and the particle is a sphere, we employ
spherical coordinates $(r,\theta,\phi)$.
The scalar gradient and the divergence can be written as:
\begin{align}
\bnabla f &= \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
\bnabla \cdot \bF &= \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
\end{align}
The scalar Laplacian can be written as:
\begin{align}
\Laplacian f = \bnabla \cdot (\bnabla f) = 
 \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
 \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
\end{align}
The vector gradient and vector Laplacian can be written as:
\begin{align}
\nonumber
\bnabla \bF &= \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, 
\\
\brhat \cdot \bLaplacian \bF &=
\Laplacian F_r - \frac{2F_r}{r^2} - 
\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}
\\
\nonumber
\bthetahat \cdot \bLaplacian \bF &= 
\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
\frac{2}{r^2}\deriv{F_r}{\theta}.
\end{align}
Note that in the spherical coordinate system,
the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
because the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
in a curvilinear coordinate system.
See Appendix \ref{append:spherical} for the full derivation of the identities above.

@@

Each discrete variable is located with respect to its cell 
as shown at Figure \ref{fig:grids}.
$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
using an all-centered grid, whereas $\bV$ is represented by its values at cell 
boundaries, using a staggered grid:
\begin{align}
\nonumber \varPhi^h_{[i,j]} &= \varPhi(\bar{r}_i, \bar{\theta}_j), \\
\nonumber C^h_{[i,j]} &= C(\bar{r}_i, \bar{\theta}_j), \\
P^h_{[i,j]} &= P(\bar{r}_i, \bar{\theta}_j), \\
\nonumber V_r^h{}_{[i,j]} &= V_r(r_i, \bar{\theta}_j), \\
\nonumber V_\theta^h{}_{[i,j]} &= V_\theta(\bar{r}_i, {\theta}_j).
\end{align}
\begin{figure}[h]
    \begin{center}
	\includegraphics[width=0.8\textwidth]{figs/grids.eps}
        \caption[Computational grid]{The computational grid is defined using
        a spherical coordinate system, due to axisymmetry of the physical problem
        and boundary conditions discretization on the particle surface.}
    \label{fig:grids}
    \end{center}
\end{figure}

@@

The derivation is performed as follows.
The nonlinear system (composed of the governing equations and the boundary conditions) 
is written as $\cO(\bx;\beta) = \bzero$.
For small $\beta$, the solution to the nonlinear system can be expanded in a Taylor series in $\beta$:
\begin{equation}
\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
\end{equation}
The nonlinear terms
are expanded around $\beta = 0$:
\begin{equation}
\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i.
\end{equation}
Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
The derivation is validated using the MATLAB symbolic toolbox by the code 
at \verb|symbolic/asymp.m| \cite{source}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic1.eps}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic2.eps}
        \caption[Ion exchanger steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
        The analytic cubic solution \eqref{eq:cubic} is represented by curves
        (solid for $\cU > 0$, dashed for $\cU < 0$), 
        and the numerical results are represented by markers 
        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
        cubic regimes match well the numerical results, including the critical $\beta$ 
        behaviour \eqref{eq:crit_beta}. 
        }
	    \label{fig:IonExCubic}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
        \caption[Quadratic convergence of steady-state velocity]{
        The discretization error between the numerical and analytical solutions for 
        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The markers represent
        the discretization errors for various grid sizes, and the dotted lines correspond to linear
        functions of $\beta$, scaled by $4^n$. 
        The graph shows that, as the number of grid points in each dimension increases by a factor of 2, 
        the discretization error decreases by a factor of 4.
        }
	    \label{fig:quadratic}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
        \caption[Highly-charged surface particle steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for highly-charged surface particle
        electrophoresis (with $\alpha = 0, \text{Du} = 0.5, \bar\zeta = 6$).
        The analytic solution velocity is represented by solid lines, 
        and the numerical results are represented by markers.
        The top figure shows the full numerical solution 
        compared to the analytical one \eqref{eq:cubic}, and
        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
        to the difference between the numerical results and the linear regime.}
	    \label{fig:Electrophoresis1}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
        \caption[Highly-charged surface particle steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for highly-charged surface particle
        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
        The analytic solution velocity is represented by solid lines, 
        and the numerical results are represented by markers.
        The top figure shows the full numerical solution 
        compared to the analytical one \eqref{eq:cubic}, and
        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
        to the difference between the numerical results and the linear regime.
        When $\beta$ is large, the analytical cubic solution loses its validity 
        because higher-order terms become significant.}
	    \label{fig:Electrophoresis2}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[128_256_512]_Rmax=10.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[512x512]_Rmax=10_30_100.eps}
        \caption[Large $\beta$ results for $\cU$]
{Large $\beta$ results for $\cU(\beta)$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
The right figure shows the numerical results of $\cU(\beta)$ for
$512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
regime of $\cU(\beta)$ is dominant. 
For moderate $\beta$ values, the steady state velocity is very close to an affine function of $\beta$.
However, for larger values of $\beta$, the numerical solution
deviates significantly from the linear regime, due to convergence problems at $\beta > 6$, 
and for $\beta \sim 7$, the solver fails to converge. The numerical convergence 
depends on the grid resolution near the particle surface -- 
as it becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver convergence improves.}
	    \label{fig:LargeBetaV_grids}	    
    \end{center}
\end{figure}
\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[512x512]_Rmax=10_30_100.eps}
        \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is the linear regime coefficient). 
The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
The right figure shows the numerical results of $\cU(\beta)$ for
$512 \times 512$ grid for $R_{max} = 100, 30, 10$.
It is seen that the difference is indeed nearly an affine function of $\beta$ in the large-$\beta$ regime, so long as the numerical solution remains sufficiently accurate.}
	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
    \end{center}
\end{figure}
\begin{figure}
    \begin{center}
    \includegraphics[width=.5\textwidth]{figs/LargeBetaRatio.eps}
        \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
        {Rate of convergence estimation for $\cU$ at large $\beta$  
        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$), 
        based on the numerical results of $\cU(\beta)$, for the grid sizes of 
        $128 \times 128$, $256 \times 256$, $512 \times 512$. 
        The rate of convergence $r(\beta)$ is estimated by 
        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$.
        For small $\beta$, $r(\beta) \rightarrow 4$, showing 
        quadratic convergence for the linear regime. 
        For moderate $\beta$, the convergence rate slows down, 
        and it deteriorates for large $\beta$ values.
        }
	    \label{fig:LargeBetaRatio}
    \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Discussion} \label{sec:discussion}
A numerical framework for a
nonlinear electrokinetic transport system is described.
The framework is used to construct numerical solvers 
for two electrokinetic problems: the migration of ion-exchangers
and surface-charged inert particle electrophoresis.
The numerical results for weak electric field 
exhibit a good correspondence to the asymptotic models as shown above.
Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
The electrophoresis problem was solved on a high-resolution grid to validate the asymptotic 
cubic correction of the steady-state velocity, as well as to provide insights into
the solution behavior for moderately strong electric fields.
For strong electric field, the nonlinear effects become dominant and
a boundary-layer structure begins to form.
Due to diminishing ion concentration $C$ at the front of the particle,
a boundary layer of thickness approximately $0.2 e^{-0.5\beta}$ 
is formed with respect to the electric field $\bE$ at the front of the particle.
The value of $E_r / \beta$ at ($r = 1$, $\theta = 0$) is given approximately by 
$e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute
(as shown in Figure \ref{fig:C_Er_product}).
However, the velocity of the particle remains nearly linear with $\beta$
and the velocity field is very close to being symmetric.

>>>>

In order to define the fluxes on the boundaries of each control volume, we employ the 
conservative formulation of the governing equations above. 
The flux terms are defined using finite differences and linear interpolation of the discrete 
variables (defined at the centroid of each cell), except for the advection flux which should not be 
discretized using linear interpolation -- due to a numerical instability 
for large cell Peclet numbers \cite{strikwerda2004finite}.

@@

\subsection{Spherical Coordinates}
Because the system is axisymmetric and the particle is a sphere, we employ
spherical coordinates $(r,\theta,\phi)$, as shown in Figure \ref{fig:SphericalCoordinateSystem}.

The scalar gradient and the divergence can be written as:
\begin{align}
\bnabla f &= \deriv{f}{r}\brhat + \frac{1}{r}\deriv{f}{\theta}\bthetahat, \\
\bnabla \cdot \bF &= \frac{1}{r^2}\deriv{}{r}\pars{F_r r^2 } + 
               \frac{1}{r \sin\theta}\deriv{}{\theta}\pars{F_\theta \sin\theta}.
\end{align}
The scalar Laplacian can be written as:
\begin{align}
\Laplacian f = \bnabla \cdot (\bnabla f) = 
 \frac{1}{r^2}\deriv{}{r}\pars{r^2 \deriv{f}{r}} + 
 \frac{1}{r^2 \sin\theta}\deriv{}{\theta}\pars{\sin\theta \deriv{f}{\theta}}.
\end{align}
The vector gradient and vector Laplacian can be written as:
\begin{align}
\nonumber
\bnabla \bF &= \deriv{F_r}{r} \brhat \brhat + \deriv{F_\theta}{r} \brhat \bthetahat + 
\frac{1}{r}\pars{\deriv{F_r}{\theta} - F_\theta} \bthetahat \brhat + 
\frac{1}{r}\pars{\deriv{F_\theta}{\theta} + F_r} \bthetahat \bthetahat, 
\\
\brhat \cdot \bLaplacian \bF &=
\Laplacian F_r - \frac{2F_r}{r^2} - 
\frac{2}{r^2 \sin\theta} \deriv{\left(F_\theta \sin\theta \right)}{\theta}
\\
\nonumber
\bthetahat \cdot \bLaplacian \bF &= 
\Laplacian F_\theta - \frac{F_\theta}{r^2 \sin^2\theta} + 
\frac{2}{r^2}\deriv{F_r}{\theta}.
\end{align}
Note that in the spherical coordinate system,
the vector Laplacian operator cannot be computed in a decoupled manner as in the Cartesian system,
because the unit vectors $\brhat, \bthetahat, \bphihat$ are functions of the coordinates
in a curvilinear coordinate system.
See Appendix \ref{append:spherical} for the full derivation of the identities above.

\begin{figure}[p]
    \begin{center}
        \includegraphics[width=0.2\textwidth]
            {figs/spherical_coordinate_system.eps}
        \caption[Spherical coordinate system]{Spherical coordinate system is employed for
        computational grid construction.}
        \label{fig:SphericalCoordinateSystem}
    \end{center}
\end{figure}

@@

Each discrete variable is located with respect to its cell 
as shown at Figure \ref{fig:grids}.
$\varPhi$, $C$ and $P$ are represented by their value at the center of each cell, 
using an all-centered grid, whereas $\bV$ is represented by its values at cell 
boundaries, using a staggered grid:
\begin{align}
\nonumber \varPhi^h_{[i,j]} &= \varPhi(\bar{r}_i, \bar{\theta}_j), \\
\nonumber C^h_{[i,j]} &= C(\bar{r}_i, \bar{\theta}_j), \\
P^h_{[i,j]} &= P(\bar{r}_i, \bar{\theta}_j), \\
\nonumber V_r^h{}_{[i,j]} &= V_r(r_i, \bar{\theta}_j), \\
\nonumber V_\theta^h{}_{[i,j]} &= V_\theta(\bar{r}_i, {\theta}_j).
\end{align}
\begin{figure}[p]
    \begin{center}
	\includegraphics[width=0.5\textwidth]{figs/grids.eps}
        \caption[Computational grid]{The computational grid is defined using
        a spherical coordinate system, due to axisymmetry of the physical problem
        and boundary conditions discretization on the particle surface.}
    \label{fig:grids}
    \end{center}
\end{figure}

@@

The derivation is performed as follows.
The nonlinear system (composed of the governing equations and the boundary conditions) 
is written as $\cO(\bx;\beta) = \bzero$.
For small $\beta$, the solution to the nonlinear system can be expanded in an asymptotic series in $\beta$:
\begin{equation}
\bx = \bx(\beta) \approx \sum_n \bx_n \beta^n.
\end{equation}
The nonlinear terms
are expanded around $\beta = 0$:
\begin{equation}
\bzero = \cO(\bx) = \sum_i \cO_i(\bx_0, \ldots \bx_i) \beta^i.
\end{equation}
Thus, the $O(\beta^k)$ term $\bx_k$ can be found recursively by solving 
$\cO_k(\bx_0, \bx_1, \ldots, \bx_k) = \bzero$,
given the previous solutions for $\bx_0, \ldots, \bx_{k-1}$.
The derivation is validated using the MATLAB symbolic toolbox by the code 
at \verb|symbolic/asymp.m| \cite{source}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic1.eps}
    \includegraphics[width=0.7\textwidth]{figs/Cubic/ionex_cubic2.eps}
        \caption[Ion exchanger steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for $\gamma < 1$ (top) and $\gamma > 1$ (bottom). 
        The analytic cubic solution \eqref{eq:cubic} is represented by curves
        (solid for $\cU > 0$, dashed for $\cU < 0$), 
        and the numerical results are represented by symbols 
        (circles for $\cU > 0$, squares for $\cU < 0$). Note that linear and
        cubic regimes match well the numerical results, including the critical $\beta$ 
        behaviour \eqref{eq:crit_beta}. 
        }
	    \label{fig:IonExCubic}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=1\textwidth]{figs/quadratic_order.eps}
        \caption[Quadratic convergence of steady-state velocity]{
        The discretization error $\hat{\cU}^h - \cU_1$ between the numerical results
        and the linear asymptotic solutions for 
        $\alpha = 0$, $\Du = 0.5$, $\bar\zeta = 6$ and $R_{max} = 100$. The symbols represent
        the discretization errors for various grid sizes, and the dotted lines correspond to linear
        functions of $\beta$, scaled by $4^n$. 
        The graph shows that, as the number of grid points in each dimension increases by a factor of 2, 
        the discretization error decreases by a factor of 4.
        }
	    \label{fig:quadratic}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.0_Du=0.5_zeta=6.0_Rmax=100.eps}
        \caption[Highly-charged surface particle steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for highly-charged surface particle
        electrophoresis (with $\alpha = 0, \text{Du} = 0.5, \bar\zeta = 6$).
        The analytic solution velocity is represented by solid lines, 
        and the numerical results are represented by symbols.
        The top figure shows the full numerical solution 
        compared to the analytical one \eqref{eq:cubic}, and
        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
        to the difference between the numerical results and the linear regime.}
	    \label{fig:Electrophoresis1}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/numerical_vs_analytical_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
    \includegraphics[width=0.6\textwidth]{figs/Electrophoresis/departure_from_linear_alpha=0.5_Du=1.0_zeta=10.0_Rmax=100.eps}
        \caption[Highly-charged surface particle steady-state velocity]{
        Steady-state velocity $\cU$ as a function of the 
        electric field magnitude $\beta$, for highly-charged surface particle
        electrophoresis (with $\alpha = 0.5, \text{Du} = 1, \bar\zeta = 10$).
        The analytic solution velocity is represented by solid lines, 
        and the numerical results are represented by symbols.
        The top figure shows the full numerical solution 
        compared to the analytical one \eqref{eq:cubic}, and
        the bottom figure compares the analytic cubic correction \cite{schnitzer2012cubic} 
        to the difference between the numerical results and the linear regime.
        When $\beta$ is large, the analytical cubic solution loses its validity 
        because higher-order terms become significant.}
	    \label{fig:Electrophoresis2}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[128_256_512]_Rmax=10.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_[512x512]_Rmax=10_30_100.eps}
        \caption[Large $\beta$ results for $\cU$]
{Large $\beta$ results for $\cU(\beta)$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$). 
The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
The right figure shows the numerical results of $\cU(\beta)$ for
$512 \times 512$ grid for $R_{max} = 100, 30, 10$. For small values of $\beta$, the linear
regime of $\cU(\beta)$ is dominant. 
For moderate $\beta$ values, the steady state velocity is very close to an affine function of $\beta$.
However, for larger values of $\beta$, the numerical solution
deviates significantly from the linear regime, due to convergence problems at $\beta > 6$, 
and for $\beta \sim 7$, the solver fails to converge. The numerical convergence 
depends on the grid resolution near the particle surface -- 
as it becomes finer (when $N_r$ increases or $R_{max}$ decreases), the solver convergence improves.}
	    \label{fig:LargeBetaV_grids}	    
    \end{center}
\end{figure}
\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[128_256_512]_Rmax=10.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaV_DeltaFromLinear[512x512]_Rmax=10_30_100.eps}
        \caption[Large $\beta$ results for $\cU$ -- difference from linear regime]
{Large $\beta$ results for $\cU(\beta) - \beta\cU_1$ ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$ and $\cU_1 \approx 4.258$ is the linear regime coefficient). 
The left figure shows the numerical results of $\cU(\beta)$ for $R_{max} = 10$ and the following grid sizes: $128 \times 128$, $256 \times 256$, $512 \times 512$. 
The right figure shows the numerical results of $\cU(\beta)$ for
$512 \times 512$ grid for $R_{max} = 100, 30, 10$.
It is seen that the difference is indeed nearly an affine function of $\beta$ in the large-$\beta$ regime, so long as the numerical solution remains sufficiently accurate.}
	    \label{fig:LargeBetaV_DeltaFromLinear_grids}	    
    \end{center}
\end{figure}
\begin{figure}
    \begin{center}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaRatio.eps}
    \includegraphics[width=.45\textwidth]{figs/LargeBetaRatio_p.eps}
        \caption[Rate of convergence estimation for $\cU$ at large $\beta$]
        {Rate of convergence estimation for $\cU$ at large $\beta$  
        ($\Du = 1$, $\bar\zeta = 10$, $\alpha = 0.5$), 
        based on the numerical results of $\cU(\beta)$, for the grid sizes of 
        $128 \times 128$, $256 \times 256$, $512 \times 512$. 
        The rate of convergence $r(\beta)$ is estimated by 
        $r(\beta) \triangleq \left(\cU^{4h}(\beta) - \cU^{2h}(\beta)\right)/\left(\cU^{2h}(\beta) - \cU^{h}(\beta)\right)$ (left). 
        The order of convergence is estimated by $p(\beta) \triangleq \log_2 r(\beta)$ (right).
        For small $\beta$, $p(\beta) \rightarrow 2$, showing 
        quadratic convergence for the linear regime. 
        For moderate $\beta$, the convergence rate slows down, 
        and it deteriorates for large $\beta$ values.
        }
	    \label{fig:LargeBetaRatio}
    \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Discussion} \label{sec:discussion}
A numerical framework for a
nonlinear electrokinetic transport system is developed.
The framework is used to construct numerical solvers 
for two electrokinetic problems: the migration of ion-exchangers
and surface-charged inert particle electrophoresis.
The numerical results for weak electric field 
exhibit a good correspondence to the asymptotic models as shown above.
Two interesting phenomena (cubic regime and downstream vortex) were predicted for the ion-exchanger
using the numerical results, and were verified using an asymptotic expansion of the nonlinear system.
The electrophoresis problem was solved on a high-resolution grid to confirm the asymptotic 
cubic correction of the steady-state velocity, as well as to provide insights into
the solution behavior for moderately strong electric fields.
For strong electric field, the nonlinear effects become dominant and
a boundary-layer structure begins to form.
Due to diminishing ion concentration $C$ at the front of the particle,
a boundary layer of thickness approximately $0.2 e^{-0.5\beta}$ 
is formed with respect to the electric field $\bE$ at the front of the particle.
The value of $E_r / \beta$ at ($r = 1$, $\theta = 0$) is given approximately by 
$e^{\beta/2}$, while the value of $C(r = 1, \theta = 0)$ is given approximately 
by $e^{-\beta/2}$, and their product remains close to 1 for all $\beta$ that we could compute
(as shown in Figure \ref{fig:C_Er_product}).
However, the velocity of the particle remains nearly linear with $\beta$
and the velocity field is very close to being symmetric.
Finally, we emphasize the importance of the analytical asymptotic derivation. This approach provides effective boundary conditions for the macroscale problem and thus eliminates the inherent physical scale disparity. This elimination enables the construction of the numerical scheme.
Furthermore, the analytical asymptotic solutions for the weak field regime enable important mutual verification of the numerical results.
